Exposure Consequences - Statistics and Figures

### 2018-02-07 ManuscriptMaterials.Rmd
added peak estimation for localization data

@@

    3. Within the workspace however, there is no interaction between movement type and training group (but there is a trend if hand angle is used as a random effect, in all analyses the 15 degree data is omitted as Denise said). Perhaps there is a small update of predicted proprioceptive consequences, that we can't parcel out. A more computational approach would be needed to see if this can explain the pattern of results here.

>>>>

## Localization peaks

Decided to add analyses to get the confidence intervals for the peaks of the localization generalization curves:

```{r localization_peaks}
getPeakLocConfidenceInterval(group='classic',CIs=c(.95), movementtype='both', LRpart='all')
getPeakLocConfidenceInterval(group='exposure',CIs=c(.95), movementtype='both', LRpart='all')
```

These results are strange: the median peak for the exposure localization is around 42 degrees. If we look at the plot, it is much higher though, somewhere between 55 and 65 probably. This doesn't change much if I only look at the passive or at the active localization data. The peak for classic makes sense though.

@@

    3. Within the workspace however, there is no interaction between movement type and training group (but there is a 'trend', p=.09, if hand angle is used as a random effect, in all analyses the 15 degree data is omitted as Denise said). Perhaps there is a small update of predicted proprioceptive consequences, that we can't parcel out. A more computational approach would be needed to see if this can explain the pattern of results here.
